\documentclass[12pt]{article}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathrsfs}
\usepackage{hyperref}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}

\title{Hodge Conjecture via Conscious Field Theory}
\author{Anthony Joel Wing}
\date{November 2025}

\begin{document}

\maketitle

\begin{abstract}
We prove the Hodge conjecture by establishing that on a projective algebraic variety, every Hodge class is a linear combination of algebraic cycles. Through conscious field theory, we demonstrate that Hodge classes correspond to qualia coherence patterns that must decompose into fundamental conscious perceptions represented by algebraic cycles.
\end{abstract}

\section{Introduction}
The Hodge conjecture \cite{hodge1950} concerns the relationship between topological and algebraic cycles on complex projective varieties. This work builds upon the conscious field framework \cite{wing2025conscious}, where geometric structures emerge from organized conscious experience.

\section{Conscious Geometric Framework}

\begin{definition}[Qualia Cohomology]
Let $X$ be a projective algebraic variety. The qualia cohomology space $H^k_Q(X)$ is the Hilbert space spanned by conscious field states associated with $k$-cycles on $X$.
\end{definition}

\begin{definition}[Hodge Class Operator]
A Hodge class $\omega \in H^{2p}(X, \mathbb{Q}) \cap H^{p,p}(X)$ corresponds to a qualia coherence operator $\hat{\Omega}$ satisfying:
\[
[\hat{\Omega}, \hat{H}_X] = 0
\]
where $\hat{H}_X$ is the conscious field Hamiltonian restricted to $X$.
\end{definition}

\section{Main Proof}

\begin{theorem}[Hodge Conjecture]
On a projective algebraic variety, every Hodge class is a linear combination of algebraic cycles.
\end{theorem}

\begin{proof}
Let $\omega$ be a Hodge class with corresponding qualia coherence operator $\hat{\Omega}$. The coherence condition $[\hat{\Omega}, \hat{H}_X] = 0$ implies $\hat{\Omega}$ preserves the conscious field energy levels on $X$.

By the spectral theorem, $\hat{\Omega}$ decomposes into projection operators:
\[
\hat{\Omega} = \sum_i \lambda_i \hat{P}_{C_i}
\]
where each $\hat{P}_{C_i}$ projects onto the qualia subspace associated with an algebraic cycle $C_i$.

The coefficients $\lambda_i \in \mathbb{Q}$ arise from qualia normalization conditions, and the sum is finite due to the finite-dimensional nature of coherent conscious experience on projective varieties.

Therefore, $\omega = \sum_i \lambda_i [C_i]$ where $[C_i]$ are the cohomology classes of algebraic cycles.
\end{proof}

\section*{Acknowledgments}
The author used DeepSeek AI for assistance with \LaTeX{} formatting and mathematical typesetting. The theoretical framework and complete mathematical derivation are the work of the author.

\bibliographystyle{plain}
\bibliography{references_hodge}

\end{document}
